---
title: "STAT 3080 — Project Part 1"
author: "Team Name Here"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: false
    number_sections: false
fontsize: 11pt
geometry: margin=1in
---

<!-- IMPORTANT: Per the announcement, make sure this exact `.Rmd` file lives in your team repository. 
Also add your team repo URL in the **References** section (not as a raw file URL). -->
<!-- Knit this file **directly to PDF** without altering the provided formatting/organization. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(knitr)
# kableExtra is optional; comment out if unavailable on your machine
suppressWarnings(suppressMessages(library(kableExtra)))
```

# Introduction

Briefly introduce your **topic** (what/why it matters beyond personal interest, 4–6 sentences).  
State the **scope** (time frame ≤ last 5 years, geography, unit of analysis).

## Research Questions

Clearly list **exactly three** specific and testable questions (bold or bullets). Each question should target **one or two parameters** (center, spread, proportion, etc.) suitable for a **single stand‑alone test in Part 2** (no regression / time‑series / predictive models). Example format:

- **RQ1.** Was *X* higher for Group A than Group B in YEAR / PERIOD?
- **RQ2.** Did the proportion of *Y* exceed *p₀* in YEAR / PERIOD?
- **RQ3.** Was the mean of *Z* different between Condition 1 and Condition 2 in YEAR / PERIOD?

Briefly (1–2 sentences each) explain the **relevance** of the three questions.

# Data summary

Describe your **data collection** and **primary sources** (≥2 primary sources total; each RQ uses variables from **at least two** primary sources). Include:

- What the sources are and **why they’re trustworthy**.  
- Whether your data are a **population** or a **sample**, and how sampled/selected.  
- Any **cleaning / modifications** and the reasons.  
- Potential **issues/biases** and expected impact.  
- A short mapping of **which variables** answer each RQ and **why appropriate**.

> **Reminder (Announcements):** Include your **team repo URL** in **References**, and for the dataset include the **original download/scrape URL** (not the raw file URL from your repo).

## Load data

Replace the path(s) below with your cleaned CSV(s). Keep raw data files in your repo as well.

```{r load-data}
# Example: load two primary-source files and join them for analysis.
# Update file names/keys as needed.
# data_src1 <- readr::read_csv("data/source1.csv")
# data_src2 <- readr::read_csv("data/source2.csv")
# joined <- data_src1 %>% 
#   inner_join(data_src2, by = c("key_var1" = "key_var2"))
# For the rest of the report, refer to the analysis data frame name you actually use:
# analysis_df <- joined
```

# Data dictionary

Provide a concise table with **variable names as used in this report** (may differ from column names), **definitions**, **units**, and **all categories** for categorical variables.

```{r data-dictionary, eval=FALSE}
# FILL THIS IN: create a tibble that describes your variables.
data_dictionary <- tibble::tibble(
  variable_name = c("var1", "var2", "group", "period"),
  description   = c("Outcome measure (units)", 
                    "Secondary measure (units)", 
                    "Group indicator (A/B definition)", 
                    "Time period definition (e.g., YYYY‑MM)")
)

kable(data_dictionary, caption = "Data dictionary") %>%
  kableExtra::kable_styling(full_width = FALSE)
```

# Data exploration

Select up to **8 summaries** total (≥2 numerical, ≥2 graphical, ≥1 per RQ). All but one per type must be **more complex than simple counts**. Create all graphics in **ggplot2** and carefully **label titles/axes/notes**.

## Example numerical summaries

```{r numerical-summaries, eval=FALSE}
# Example: group-wise means/SDs
# analysis_df %>% 
#   group_by(group) %>% 
#   summarise(
#     mean_outcome = mean(var1, na.rm = TRUE),
#     sd_outcome   = sd(var1, na.rm = TRUE),
#     n            = dplyr::n()
#   ) %>%
#   kable(caption = "Group-wise summary of var1") %>%
#   kableExtra::kable_styling(full_width = FALSE)
#
# Example: two-parameter table by period
# analysis_df %>% 
#   group_by(period) %>% 
#   summarise(
#     mean_var1 = mean(var1, na.rm = TRUE),
#     sd_var1   = sd(var1, na.rm = TRUE),
#     prop_A    = mean(group == "A", na.rm = TRUE)
#   ) %>%
#   kable(caption = "Period summaries of key parameters") %>%
#   kableExtra::kable_styling(full_width = FALSE)
```

## Example graphical summaries

```{r plots, eval=FALSE, fig.height=3.5, fig.width=6}
# Histogram / density
# ggplot(analysis_df, aes(x = var1)) +
#   geom_histogram(binwidth = 5) +
#   labs(title = "Distribution of var1", x = "var1 (units)", y = "Count",
#        caption = "Note: binwidth illustrative; adjust per data.") +
#   theme_minimal()

# Boxplot by group
# ggplot(analysis_df, aes(x = group, y = var1)) +
#   geom_boxplot() +
#   labs(title = "var1 by group", x = "Group", y = "var1 (units)") +
#   theme_minimal()

# Line plot over time (if applicable)
# ggplot(analysis_df, aes(x = period, y = var1, group = 1)) +
#   geom_line() + geom_point() +
#   labs(title = "var1 over time", x = "Period", y = "var1 (units)") +
#   theme_minimal()
```

## Tie each summary to an RQ

After each table/figure, add 1–2 sentences explaining what it shows and **which RQ** it informs.

# Conclusions

Provide a **clear narrative** that interprets the displayed summaries (values/patterns/trends) and what they **may imply** for the topic.  
State which **one** of your RQs appears **most interesting** to analyze in **Part 2** and why.  
**Do not** do inferential testing here.

# Data appendix

Begin on a **new page**. Show a readable table of the **first 10–20 rows** of the analysis data.

```{r appendix, eval=FALSE}
# analysis_df %>% head(20) %>% 
#   kable(caption = "First 20 rows of analysis data") %>%
#   kableExtra::kable_styling(full_width = FALSE)
```

# References

Use any standard format (APA/MLA/etc.). Start on a **new page**. Include both **background** sources and **primary data sources**. In the report body, add inline citations where appropriate.

- Team repository URL: <https://github.com/your-org/your-repo>  <!-- Use your repo homepage URL (not a raw file URL) -->
- Primary Source 1 (original download page): <https://...>
- Primary Source 2 (original download page): <https://...>
- Additional background refs...
